Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-13 paper/ms.tex
caveats

There are two important caveats for the work presented here. The first is the
assumption of a single LAE per dark matter halo. It is expected
for sub-halos in the simulation to host satellited galaxies. However,
it has been found in analysis based on the shape of the correlation
function [citation needed] that satellite galaxies are not a dominant
population, making our initial approximation a reasonable one.

The second caveat are the precise values for the mass intervals. These
numbers are defined from the halos defined in using the BDM halo
finder with a density threshold of 200 times the critical
density. Different halo finders and definitions for the detection
density threshold can yield different masses up to a factor of 2
[citation needed].

>>>>

There are two important caveats for the work presented here. The first is the
assumption of a single LAE per dark matter halo. It is expected
for sub-halos in the simulation to host satellited galaxies. However,
it has been found in analysis based on the shape of the correlation
function \citep{Jose2013b} that satellite galaxies are not a dominant
population, making our initial approximation a reasonable one.

The second caveat are the precise values for the mass intervals. These
numbers are defined from the halos defined in using the BDM halo
finder with a density threshold of 200 times the critical
density. Different halo finders and definitions for the detection
density threshold can yield different masses up to a factor. For
instance a Friends-of-Friends algorithm with linking lenght $l=0.20$
times the average interparticle distance finds halos on average $1.4$
times more massive than BDM halos \citep{Bolshoi}. Therefore, the mass
values for $M_{\rm min}$ and $M_{\rm max}$ must be considered exact
within $\sim 0.2$ dex.
